---
title: "R Notebook"
output: html_notebook
---

# Preliminaries

## Libraries & Dependencies
```{r}
library(tidyverse)
library(lme4)
library(brms)
library(wesanderson)
library(ggparty)
library(partykit)

source("survey.R")
source("helpers.R")
```

## Data Read-in

```{r}
data <- read_csv("news_indexicality_main-merged.csv")
data <- extract_demographics(data, "workerid", "response") # This script extracts information from the "Demographic" type trial and appends it to the participants' responses
data <- extract_likert(data, "workerid","response")
```

## Coding Data

```{r}
data <- data %>% 
  mutate(
    conResponse = ifelse(result == "Fox News",1,0), # Convert 'FoxNews' Responses to binary
    progResponse = ifelse(result == "MSNBC",1,0), # Convert 'MSNBC' Responses to binary
    modResponse = ifelse(result == "NPR",1,0), # Convert 'NPR' Responses to binary
    modifierType = ifelse(refExp %in% c("Transgender Woman","Transgender Man"),"Transgender",ifelse(refExp %in% c("Trans Woman","Trans Man"),"Trans","Biological")), # Code macrocategories for each of the modifiers
    Q0 = as.numeric(Q0), 
    politicalTernary = case_when( ## Bin participants into "Democrat", "Republican", and "Moderate"
      Q0 %in% c(0,1) ~ "Dem",
      Q0 %in% c(3,4) ~ "Rep",
      Q0 == 2 ~ "Moderate",
      TRUE ~ "Declined"
    )
  )
```

## Attention Checks

Participants who fail more than 1 attention check question are excluded from analysis. This leaves us with 183 participants whose data we can use in analysis.

```{r}
attentionTrials <- data %>% 
  filter(dataType == "Attention") %>% 
  mutate(attentionCheck = ifelse(correct.x == result,1,0)) %>% 
  group_by(workerid,political) %>% 
  summarize(
    meanAttention = mean(attentionCheck)
  ) %>% 
  select(c("workerid","meanAttention","political")) %>% 
  filter(meanAttention < 0.8)
  
exclusion <- attentionTrials$workerid

data <- data %>% 
  filter(!(workerid) %in% exclusion)
```

## DataSet Creation

Separate out critical trials from filler trials
```{r}
CriticalData <- data %>% 
  filter(dataType == "Critical")

fillerTrials <- data %>% 
  filter(dataType == "Filler") %>% 
  mutate(source = case_when( # Because a handful of fillers were actually CNN, let's rename them to "Left-Wing" and then rename the other variables to concord
    source %in% c("CNN","PinkNews") ~ "Left-Wing",
    source == "Breitbart" ~ "Right-Wing",
    source == "NPR" ~ "Moderate"
  )
  )
```

# Filler Trial Analysis

## Conservative

```{r}
fillerTrials %>% 
  group_by(source) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>% 
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>%
  ggplot(aes(x=source,y=meanConResponse,fill=source)) +
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") +
  theme_bw() + 
  theme(legend.position="none") + 
  ylim(0,1) + 
  labs(x="Headline Leaning",y="Proportion of 'Fox News' Responses") + 
  scale_fill_manual(values = wes_palette("IsleofDogs1"))
```

```{r}
fillerTrials %>% 
  filter(politicalTernary!= "Declined") %>% 
  group_by(source,politicalTernary) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>% 
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>%
  ggplot(aes(x=source,y=meanConResponse,fill=source)) +
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") +
  theme_bw() + 
  theme(legend.position="none") + 
  ylim(0,1) + 
  labs(x="Headline Leaning",y="Proportion of 'Fox News' Responses") + 
  scale_fill_manual(values = wes_palette("IsleofDogs1")) + 
  facet_wrap(~politicalTernary, scales="free_x")
```

## Progressive

```{r}
fillerTrials %>% 
  filter(politicalTernary != "Declined") %>% 
  group_by(source,politicalTernary) %>% 
  summarize(
    responseCount = n(),
    meanProgResponse = mean(progResponse),
    CI.Low = ci.low(progResponse),
    CI.High = ci.high(progResponse),
  ) %>% 
  mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>%
  ggplot(aes(x=source,y=meanProgResponse,fill=source)) +
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") +
  theme_bw() + 
  theme(legend.position="none") + 
  ylim(0,1) + 
  labs(x="Headline Leaning",y="Proportion of 'MSNBC' Responses") + 
  scale_fill_manual(values = wes_palette("IsleofDogs1")) + 
  facet_wrap(~politicalTernary, scales="free_x")
```

## Moderate


```{r}
fillerTrials %>% 
  filter(politicalTernary != "Declined") %>% 
  group_by(source,politicalTernary) %>% 
  summarize(
    responseCount = n(),
    meanModResponse = mean(modResponse),
    CI.Low = ci.low(modResponse),
    CI.High = ci.high(modResponse),
  ) %>% 
  mutate(YMin = meanModResponse - CI.Low, YMax = meanModResponse + CI.High) %>%
  ggplot(aes(x=source,y=meanModResponse,fill=source)) +
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") +
  theme_bw() + 
  theme(legend.position="none") + 
  ylim(0,1) + 
  labs(x="Headline Leaning",y="Proportion of 'NPR' Responses") + 
  scale_fill_manual(values = wes_palette("IsleofDogs1")) + 
  facet_wrap(~politicalTernary, scales="free_x")
```




# Pre-Registered Model Analyses

## Conservative Model

### Data Subset

```{r}
conModelData <- CriticalData %>% 
  filter(politicalTernary %in% c("Dem","Rep")) %>%
  mutate(politicalTernary = fct_relevel(politicalTernary, "Dem"))

contrasts(conModelData$politicalTernary)
```

### Model

```{r}
m.b <- brm(conResponse ~ modifierType*source*politicalTernary + (1|workerid) + (1|item), data = conModelData, family=bernoulli(link="logit"), iter = 2000)
```

```{r}
summary(m.b)
```

```{r}
plot(m.b)
```

```{r}
h <- hypothesis(m.b, "b_modifierTypeTransgender:politicalTernaryRep < 0")
print(h, digits=4)
```

### Plots

```{r}
CriticalData %>% 
  # mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>%
  filter(politicalTernary %in% c("Rep","Dem")) %>%  # Uncomment when faceting by political
  group_by(modifierType) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  # facet_grid(~politicalTernary, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  # mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>%
  filter(politicalTernary %in% c("Rep","Dem","Moderate")) %>%  # Uncomment when faceting by political
  group_by(modifierType,politicalTernary) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_grid(~politicalTernary, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>%
  filter(politicalTernary %in% c("Rep","Dem")) %>%  # Uncomment when faceting by political
  group_by(modifierType,politicalTernary,ageGroup) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_grid(ageGroup~politicalTernary, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```
```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>%
  filter(politicalTernary %in% c("Rep","Dem")) %>%  # Uncomment when faceting by political
  group_by(modifierType,politicalTernary,ageGroup) %>% 
  summarize(
    responseCount = n(),
    meanProgResponse = mean(progResponse),
    CI.Low = ci.low(progResponse),
    CI.High = ci.high(progResponse),
  ) %>%
  mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanProgResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "MSNBC" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_grid(ageGroup~politicalTernary, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>%
  filter(politicalTernary %in% c("Rep","Dem")) %>%  # Uncomment when faceting by political
  group_by(modifierType,politicalTernary,ageGroup) %>% 
  summarize(
    responseCount = n(),
    meanModResponse = mean(modResponse),
    CI.Low = ci.low(modResponse),
    CI.High = ci.high(modResponse),
  ) %>%
  mutate(YMin = meanModResponse - CI.Low, YMax = meanModResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanModResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "NPR" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_grid(ageGroup~politicalTernary, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>%
  filter(!is.na(Q0)) %>% 
  # filter(politicalTernary %in% c("Rep","Dem")) %>%  # Uncomment when faceting by political
  group_by(modifierType,Q0) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_grid(~Q0, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  mutate(Q1 = as.numeric(Q1)) %>%
  filter(!is.na(Q1),
  politicalTernary != "Declined") %>% 
  group_by(politicalTernary) %>% 
  summarize(
    responseCount = n(),
    meanFoxConsumption = mean(Q1),
    CI.Low = ci.low(Q1),
    CI.High = ci.high(Q1),
  ) %>%
  mutate(YMin = meanFoxConsumption - CI.Low, YMax = meanFoxConsumption + CI.High) %>% 
  ggplot(aes(x=politicalTernary,y=meanFoxConsumption,fill=politicalTernary)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  scale_fill_manual(values=wes_palette("AsteroidCity3")) + 
  theme_bw()
```

```{r}
CriticalData %>% 
  mutate(Q2 = as.numeric(Q2)) %>%
  filter(!is.na(Q2),
  politicalTernary != "Declined") %>% 
  group_by(politicalTernary) %>% 
  summarize(
    responseCount = n(),
    meanMSBCConsumption = mean(Q2),
    CI.Low = ci.low(Q2),
    CI.High = ci.high(Q2),
  ) %>%
  mutate(YMin = meanMSBCConsumption - CI.Low, YMax = meanMSBCConsumption + CI.High) %>% 
  ggplot(aes(x=politicalTernary,y=meanMSBCConsumption,fill=politicalTernary)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  scale_fill_manual(values=wes_palette("AsteroidCity3")) + 
  theme_bw()
```

### Demographic Analysis

```{r}
CriticalData %>% 
  mutate(
    ageGroup = ifelse(age >= 40, "Older","Younger")
  ) %>% 
  select(c("workerid","ageGroup","politicalTernary")) %>% 
  unique() %>% 
  group_by(ageGroup,politicalTernary) %>% 
  summarize(
    partitipantCount = n()
  )
```


## Progressive Model

### Data Subset


```{r}
progModelData <- CriticalData %>% 
  filter(politicalTernary %in% c("Dem","Rep")) %>%
  mutate(politicalTernary = fct_relevel(politicalTernary, "Dem"))

contrasts(progModelData$politicalTernary)
```

### Model

```{r}
m.b <- brm(progResponse ~ modifierType*source*politicalTernary + (1|workerid) + (1|item), data = progModelData, family=bernoulli(link="logit"), iter = 2000)
```

```{r}
summary(m.b)
```

```{r}
plot(m.b)
```

```{r}
h <- hypothesis(m.b, "sourcePinkNews > 0")
print(h, digits=4)
```




## Moderate Model

### Data Subset




```{r}
CriticalData %>% 
  # filter(!political %in% c("Independent","Moderate")) %>%  # Uncomment when faceting by political
  group_by(refExp,refGender) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=refExp,y=meanConResponse, fill=refGender)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Political Party', y='Mean Fox News Consumption Score', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity3")[2:4]) + 
  # facet_wrap(~refGender, scales="free_x") +
  # facet_grid(political~refGender, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```




## Progressive Responses

### Plot

# ```{r}
# CriticalData %>% 
#   group_by(refExp,refGender,lgbt) %>% 
#   summarize(
#     responseCount = n(),
#     meanProgResponse = mean(progResponse),
#     CI.Low = ci.low(progResponse),
#     CI.High = ci.high(progResponse),
#   ) %>%
#   mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>% 
#   ggplot(aes(x=refExp,y=meanProgResponse, fill=refGender)) + 
#   geom_bar(stat = "identity", position="dodge") + 
#   geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
#   geom_hline(yintercept = 0.33, linetype="dashed", color = "red") + 
#   # coord_flip() + 
#   labs(x='Referring Expression', y='Proportion of "MSNBC" Responses', fill='Gender of Referring Expression') + 
#   theme_bw() + 
#   theme(legend.position="bottom") + 
#   scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
#   facet_wrap(~lgbt)
# ```

```{r}
CriticalData %>% 
  # filter(!political %in% c("Independent","Moderate")) %>% # uncomment when faceting by political
  group_by(refExp) %>% 
  summarize(
    responseCount = n(),
    meanProgResponse = mean(progResponse),
    CI.Low = ci.low(progResponse),
    CI.High = ci.high(progResponse),
  ) %>%
  mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=refExp,y=meanProgResponse, fill=refGender)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Referring Expression', y='Proportion of "MSNBC" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  # facet_grid(political~refGender, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

### Model

```{r}
progModel <- brm(progResponse ~ refExp,data=CriticalData)
```

```{r}
summary(progModel)
```


## Moderate Responses

### Plot

```{r}
CriticalData %>% 
  group_by(refExp, refGender) %>% 
  summarize(
    responseCount = n(),
    meanModResponse = mean(modResponse),
    CI.Low = ci.low(modResponse),
    CI.High = ci.high(modResponse),
  ) %>%
  mutate(YMin = meanModResponse - CI.Low, YMax = meanModResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=refExp,y=meanModResponse, fill = refGender)) + 
  geom_bar(stat = "identity", position="dodge") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "red") +
  labs(x='Referring Expression', y='Proportion of "NPR" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~refGender, scales="free_x") + 
  ylim(0,1)
```

```{r}
CriticalData %>% 
  summarize(
    meanConResponse = mean(conResponse),
    meanProgResponse = mean(progResponse),
    meanModResponse = mean(modResponse)
  ) 
```


# Miscellaneous

## Participant Comments

```{r}
data %>% 
  filter(comments != "") %>% 
  select(c("workerid","comments")) %>% 
  group_by(workerid,comments) %>% 
  unique()
```

## Proportion of Political 

```{r}
data %>% 
  select(c("workerid","politicalTernary","gender")) %>% 
  group_by(workerid,politicalTernary,gender) %>% 
  unique() %>% 
  group_by(politicalTernary,gender) %>% 
  summarize(count = n())
```

## LGBT

```{r}
data %>% 
  select(c("workerid","lgbt")) %>% 
  group_by(workerid,lgbt) %>% 
  unique() %>% 
  group_by(lgbt) %>% 
  summarize(count = n())
```

```{r}
CriticalData %>% 
  filter(lgbt != "Decline to state") %>% 
  group_by(modifierType,lgbt) %>% 
  # filter(!political %in% c("Independent","Moderate")) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Referring Expression', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  # facet_wrap(~refGender, scales="free_x") + 
  facet_grid(~lgbt, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```


# By Item Effects

```{r}
CriticalData %>% 
  mutate(source = ifelse(source=="CNN","PinkNews",source)) %>% 
  group_by(item,modifierType) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  ggplot(aes(x=modifierType,y=meanConResponse)) + 
  geom_bar(stat="identity",position="dodge") + 
  geom_hline(yintercept = 0.33, linetype="dashed", color = "red") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  theme_bw() + 
  scale_fill_manual(values=wes_palette("AsteroidCity2")[3:4])+
  facet_wrap(~item, scales = "free_x")
  # facet_wrap(~refGender)
```

```{r}
CriticalData %>% 
  mutate(source = ifelse(source=="CNN","PinkNews",source)) %>% 
  group_by(item,source) %>% 
  summarize(
    responseCount = n(),
    meanProgResponse = mean(progResponse),
    CI.Low = ci.low(progResponse),
    CI.High = ci.high(progResponse),
  ) %>%
  mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>% 
  ggplot(aes(x=reorder(item,-meanProgResponse),y=meanProgResponse,fill=source)) + 
  geom_bar(stat="identity",position="dodge") + 
  geom_hline(yintercept = 0.33, linetype="dashed", color = "red") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  theme_bw() + 
  scale_fill_manual(values=wes_palette("AsteroidCity2")[3:4])
```



```{r}
CriticalData %>% 
  mutate(source = ifelse(source=="CNN","PinkNews",source)) %>% 
  group_by(item,source) %>% 
  summarize(
    responseCount = n(),
    meanModResponse = mean(modResponse),
    CI.Low = ci.low(modResponse),
    CI.High = ci.high(modResponse),
  ) %>%
  mutate(YMin = meanModResponse - CI.Low, YMax = meanModResponse + CI.High) %>% 
  ggplot(aes(x=reorder(item,-meanModResponse),y=meanModResponse,fill=source)) + 
  geom_bar(stat="identity",position="dodge") + 
  geom_hline(yintercept = 0.33, linetype="dashed", color = "red") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  theme_bw() + 
  scale_fill_manual(values=wes_palette("AsteroidCity2")[3:4])
```

### Age

```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>% 
  # filter(!political %in% c("Independent","Moderate")) %>%  # Uncomment when faceting by political
  group_by(modifierType,ageGroup) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse, fill=ageGroup)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Referring Expression', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~ageGroup, scales="free_x") +
  # facet_grid(~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>% 
  # filter(!political %in% c("Independent","Moderate")) %>%  # Uncomment when faceting by political
  group_by(modifierType,ageGroup) %>% 
  summarize(
    responseCount = n(),
    meanProgResponse = mean(progResponse),
    CI.Low = ci.low(progResponse),
    CI.High = ci.high(progResponse),
  ) %>%
  mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanProgResponse, fill=ageGroup)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Referring Expression', y='Proportion of "MSNBC" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~ageGroup, scales="free_x") +
  # facet_grid(~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```


```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>% 
  # filter(!political %in% c("Independent","Moderate")) %>%  # Uncomment when faceting by political
  group_by(modifierType,ageGroup) %>% 
  summarize(
    responseCount = n(),
    meanModResponse = mean(modResponse),
    CI.Low = ci.low(modResponse),
    CI.High = ci.high(modResponse),
  ) %>%
  mutate(YMin = meanModResponse - CI.Low, YMax = meanModResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanModResponse, fill=ageGroup)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Referring Expression', y='Proportion of "MSNBC" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~ageGroup, scales="free_x") +
  # facet_grid(~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

## Collapsed Modifier


```{r}
CriticalData %>% 
  # mutate(ageGroup = ifelse(age <= 35, "younger","older")) %>% 
  # filter(!political %in% c("Independent","Moderate")) %>%  # Uncomment when faceting by political
  group_by(modifierType) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  # facet_wrap(~political, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  # mutate(ageGroup = ifelse(age <= 35, "younger","older")) %>% 
  filter(politicalTernary %in% c("Dem","Rep")) %>%  # Uncomment when faceting by political
  group_by(modifierType,politicalTernary) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~politicalTernary, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  # mutate(ageGroup = ifelse(age <= 35, "younger","older")) %>% 
  filter(political %in% c("Progressive","Conservative")) %>%  # Uncomment when faceting by political
  group_by(modifierType,political) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~political, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```


```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>%
  filter(political %in% c("Progressive","Conservative")) %>%  # Uncomment when faceting by political
  group_by(modifierType,political,ageGroup) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  # facet_wrap(~political, scales="free_x") +
  facet_grid(ageGroup~political, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```


```{r}
CriticalData %>% 
  # mutate(ageGroup = ifelse(age <= 35, "younger","older")) %>% 
  # filter(!political %in% c("Independent","Moderate")) %>%  # Uncomment when faceting by political
  group_by(modifierType) %>% 
  summarize(
    responseCount = n(),
    meanProgResponse = mean(progResponse),
    CI.Low = ci.low(progResponse),
    CI.High = ci.high(progResponse),
  ) %>%
  mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanProgResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "MSNBC" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  # facet_wrap(~political, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  group_by(modifierType) %>% 
  mutate()
```



```{r}
CriticalData %>% 
  mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>%
  filter(political %in% c("Progressive","Conservative")) %>%  # Uncomment when faceting by political
  group_by(modifierType,political) %>% 
  summarize(
    responseCount = n(),
    meanProgResponse = mean(progResponse),
    CI.Low = ci.low(progResponse),
    CI.High = ci.high(progResponse),
  ) %>%
  mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanProgResponse,fill=modifierType)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Modifier Type', y='Proportion of "MSNBC" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~political, scales="free_x") +
  # facet_grid(gender~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

### Conditional Inference Testing

```{r}
predictorsOnly <- CriticalData %>% 
  filter(political %in% c("Progressive","Conservative")) %>% 
  select(c("conResponse","modifierType","source","political")) %>% 
  mutate(
    modifierType = as.factor(modifierType),
    source = as.factor(source),
    political = as.factor(political),
    conResponse = as.factor(conResponse)
  )

prop.table(table(CriticalData$modifierType))
```

```{r}
conConInfTree <- partykit::ctree(
  conResponse ~ .,
  data = predictorsOnly,
  control = ctree_control(testtype = "Teststatistic",
                          maxdepth = 2)
)
```

```{r}
condConTree <- ggparty(conConInfTree, layout =) +
  geom_edge() +
  geom_edge_label() +
  geom_node_label(
    line_list = list(
      aes(label = splitvar),
      aes(label = paste("N =", nodesize))
    ),
    line_gpar = list(
      list(size = 13),
      list(size = 10)
    ),
    ids = "inner"
  ) +
  geom_node_label(aes(label = paste0("Node ", id, ", N = ", nodesize)),
    ids = "terminal", nudge_y = -0.3, nudge_x = 0.01
  ) +
  geom_node_plot(
    gglist = list(
      geom_bar(aes(x = "", fill = conResponse),
        position = position_fill(), color = "black"
      ),
      theme_minimal(),
      scale_fill_manual(values = c("red", "grey"), guide = FALSE),
      scale_y_continuous(breaks = c(0, 1)),
      xlab(""), ylab("proportion declined"),
      geom_text(aes(
        x = "", group = conResponse,
        label = stat(count)
      ),
      stat = "count", position = position_fill(), vjust = 1.7
      )
    ),
    shared_axis_labels = TRUE
  )
```

```{r}
ggsave("images/condConTree.png", plot=condConTree, width=20, height=12)
```

```{r}
CriticalData %>% 
  group_by(age,workerid) %>% 
  unique() %>% 
  ggplot(aes(x=age)) + 
  geom_histogram(stat="count")
```


```{r}
CriticalData %>% 
  # mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>% 
  # filter(!political %in% c("Independent","Moderate")) %>%  # Uncomment when faceting by political
  group_by(modifierType,source) %>% 
  summarize(
    responseCount = n(),
    meanConResponse = mean(conResponse),
    CI.Low = ci.low(conResponse),
    CI.High = ci.high(conResponse),
  ) %>%
  mutate(YMin = meanConResponse - CI.Low, YMax = meanConResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanConResponse, fill=source)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Referring Expression', y='Proportion of "Fox News" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~source, scales="free_x") +
  # facet_grid(~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```

```{r}
CriticalData %>% 
  # mutate(ageGroup = ifelse(age <= 40, "younger","older")) %>% 
  # filter(!political %in% c("Independent","Moderate")) %>%  # Uncomment when faceting by political
  group_by(modifierType,source) %>% 
  summarize(
    responseCount = n(),
    meanProgResponse = mean(progResponse),
    CI.Low = ci.low(progResponse),
    CI.High = ci.high(progResponse),
  ) %>%
  mutate(YMin = meanProgResponse - CI.Low, YMax = meanProgResponse + CI.High) %>% 
  # select(c("refExp","meanConResponse"))
  ggplot(aes(x=modifierType,y=meanProgResponse, fill=source)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25) +
  geom_hline(yintercept = 0.33, linetype="dashed", color = "black") + 
  # coord_flip() + 
  labs(x='Referring Expression', y='Proportion of "MSNBC" Responses', fill='Gender of Referring Expression') + 
  theme_bw() + 
  theme(legend.position="none") + 
  scale_fill_manual(values=wes_palette("AsteroidCity1")) + 
  facet_wrap(~source, scales="free_x") +
  # facet_grid(~ageGroup, scales="free_x") + # Add political to group_by()
  ylim(0,1)
```


```{r}
politicalProgs <- CriticalData %>%
  filter(political == "Progressive") %>% 
  mutate(ageGroup = ifelse(age <= 30, "younger","older"))
```


```{r}
brm(conResponse~ageGroup + (1|workerid) + (1|item), data = politicalProgs)
```


```{r}
CriticalData %>% 
  select(c("workerid","political","politicalTernary")) %>% 
  group_by(workerid,political,politicalTernary) %>% 
  unique() %>% 
  group_by(political,politicalTernary) %>% 
  summarize(
    count=n()
  )
```


```{r}
summary(data)
```





